---
title: "Lab 5"
author: "German Silva"
date: "10/26/2021"
output: 
  html_document: 
    toc: yes
    theme: cerulean
    number_sections: yes
---

<!-- my code folding wasn't working when I tried so it doesn't appear here -->

```{r setup, include=TRUE, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Attach package
library(tidyverse)
```

# Confidence intervals

In this section we'll leran to use the `t.test()` function as a way to returnthe confidence interbal using the t-distribution.

## Example 1

create a mock sample of observation values, and find the confidence interval. Then we'll learn how to report that. 
```{r}
pika_mass <- c(76, 85, 100, 78, 94, 88, 83, 111) # creation of mock sample

pika_mean <- mean(pika_mass)

pika_sd <- sd(pika_mass)

pika_ci <- t.test(pika_mass)

pika_ci # not a good way of reporting
```

### Risky and tedious way: 

Mean pika mass at Paiute Pass is 86.29 g $\pm$ 8.54 g (mean $\pm$ 1 standard deviation, n=7) with a 95% confidence interval of [78.39, 94.18] g. 

### A high initial investment, but safer & better way

#### In-line code referencing to stored objects!

<!-- Use a single backtick on either side of a lowercase r to create an in-line bit of code. -->

Mean pika at Paiute Pass is `r round(pika_mean, 2)` g $\pm$ `r round(pika_sd, 2)` g (mean $\pm$ 1 standard deviation, n = `r length(pika_mass)`) with a 95% confidence interval of [`r round(pika_ci$conf.int, 2)`].


<!-- how to call specific vector positions from lists: my_list$name[2]
     you can just call from data frames/vectors like my_list$age
-->


# Two-Sample T-test

Use a two-sample t-test to test the naull hypothesis that samples were drawn from populations with the same mean (difference in means = 0).

- H0: means difference = 0
- HA: Means difference is NOT = 0

This is a two-sided t-test because no directionality is implied

## Example 1

```{r}
oak_trees <- c(20, 15, 12, 27, 8, 11, 16, 23)

pine_trees <- c(48, 60, 73, 52, 44, 57, 35, 18)
```

Is there a significant difference in mean heights for oak and pine trees?

```{r}
trees_t <- t.test(oak_trees, pine_trees)
```

The p-value of `r round(trees_t$p.value, 5)` means that there is a `r round(trees_t$p.value * 100, 3)` chance that if the mean height of the two populations are the same the sample means would be at least this different. 

Therefore, we reject the null hypothesis that the two tree populations have the same mean height. 

## Example 2

Using the `mpg` dataset to compare city gas mileage for SUVs and compact cars. 

```{r}
# create a subset called compact_suv that only contains observations where the class is suv OR compact

compact_suv <- mpg %>% 
  filter(class %in% c('suv', 'compact'))
```

```{r}
ggplot(data = compact_suv, aes(x= cty)) +
  geom_histogram(bins = 12) +
  facet_wrap(~ class)

# Quantile- Quantile plot
ggplot(data = compact_suv, aes(sample = cty)) +
  geom_qq() +
  facet_wrap(~ class)
```

```{r}
compact_suv_summary <- compact_suv %>% 
  group_by(class) %>% 
  summarize(mean_city = mean(cty),
            sd_cty = round(sd(cty), 1),
            sample_size = n())

compact_suv_summary
```

